### 2018-04-18 paper_wc_4-12.tex
Moving PhD paper from Dropbox to github.

In applying a distributed PSP implementation to CMHK market, we
find that
the market is able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and design our mechanism tp provide the functions
for effective communication between the connected users. We claim that in
this secondary market our formulation holds the desired VCG qualities through the construction of a
probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.

@@

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in the CMHK market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many ISPs each holding
thier own local auction; there is no entity that holds a global market knowledge.

@@

(MOVED: TO ORGANIZE)\\
The main contribution of this work 
is an auction mechanism inspired by the classic PSP throughput problem. In
order to apply a distributed PSP implementation to the CMHK market,
we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the communication
expense from numerous local auctions trading an infinitely divisible resource.
We will assume that the cost of participating in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. It is worth mentioning that CMHK users are not allowed to resell data
purchased from the CMHK
market, additionally, the purchased data does not carry to the next
service period. Therefore, a market equilibrium, where
supply equals demand, requires that users maintain incentive for truthfullness
across a distributed setting.
We complete a comprehensive analysis of market dynamics, (FINISH)
To the best of our knowledge, this is the first work to provide a truthful
mechanism in a distributed setting for data-exchange based on market behavior.
\\
\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
restrictions introduced by the CMHK secondary market. We reserve this for
future work.

We claim that the CMHK market is
able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and as our mechanism provides
for effective communication between the connected users.

Despite the small message space, with many user types, there is no single
way to do the transformation from the direct revelation mechanism to the
desired one. Our mechanism is naturally designed by guessing
right direct-revelation-to-desired-mechanism transformation and building it
into the allocation rule to be the primary step in the design. This incentive for a user to
truthfully reveal its type is built into the user strategies. As in classic
mechanism design, we determine the equilibria as result of incentive
compatibility in our mechanism design. 
We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem.

This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space.

@@

Progressive second price auctions (PSPs) were proposed
in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
scheme to provide consistent services for network bandwith users.
\cite{diffserve} conducts a game theoretic analysis, deriving
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria based on their game-theoretic
model. Constructing necessary and sufficient conditions for the stability
of the game allows the sustainability of any set
of service level agreement configurations between Internet service
providers.

@@

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.

@@

\section{The Problem Model}

\subsection{The CMHK Market}

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$, and that the user valuation
\iffalse
is independently and identically
distributed (i.i.d.) and
\fi
satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
separated (a seller does not also buy data and vice versa). Thus, we may assume
that this is implied in our notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
$j$. For the purposes of our analysis, we will assume that a zero bid from a
buyer is equivalent to no bid.
A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
with the intent of offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$.

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
$i$ gains access to the full grid $s$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

@@

We assume that the CMHK market does not have network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
bandwidth in wireless networks is not the focus of this paper. We
conduct a comprehensive analysis, deriving a globally optimal strategy suited for
users with local information in a distrubuted data-sharing model. 
Users in the CMHK market do not need to bid on a complete ``route", as in the
bandwidth allocation problem \cite{semret}. Instead, our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
will determine its bid quanities by,
\begin{equation}\label{opt-out}
    e_i(a) = [e_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, this abstraction applies our \emph{user strategy}
to the PSP rules.
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is now of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
the buyers' valuation of allocation $a$ across local markets (and thus multiple sellers).
In this way we extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

The sellers, $j\in\mcI$ are not associated with an opt-out function, we
consider their valuation to be a functional extension of the buyers, where
$\theta^j$ is constructed by buyer demand.
The sellers strategy can only be to determine the reserve price of their local
auction, using only information from buyers who have not opted out.
In our analysis, we demonstrate market dynamics, and further show evidence of symmetry in the strategies of
buyers and sellers.

\subsubsection{Market Dynamics}
The buyer demand largely motivates the market price function, however, the
distributed nature of the market prevents any single user from knowing the
market demand for a quantity of data. All users have knowledge of market
supply, as this is public information, however only buyers
are able to determine supply or demand across multiple auctions after time $t=0$, and then only from auctions
in which they participate. \\
\textbf{Remark:}
It is possible that a seller would be able to derive information about other
auctions by examining buyer bids over time, particularly if the seller had knowledge of the
buyer strategy. (FUTURE WORK?)\\
In order to represent the public platform of the secondary market, we model the ISP as
a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
in any auctions. At time $t=0$, a seller $k$ entering the market will have submitted bid
$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform.

A given demand may lead to diffent prices, which emerge directly from the users valuation
of the resources and, possibly, their decision strategies. The seller does not
require a priori demand information.
It is worth mentioning that the \emph{analysis} of the auction as
a game assumes some forms of demand and supply, to derive properties.
The mechanism itself does not require any knowledge of user demand or
valuation. 
\iffalse
The ISP overage
charge inducing an upper bound on the sellers' reserve prices implies that
supply will always be greater than demand, thereby reducing the sellers'
influence on market dynamics.
\fi

As the buyer valuation is elastic, even infinitesimal changes in the market dynamics can be
modeled. This, and the homogenous nature of data in the CMHK market, 
allows for the analysis of additional constraints imposed by the user
strategies. Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
A buyers' valuation of an amount of data represents how much a buyer is willing
to pay for that amount. 
This is equivalent to the bid price that
satisfies $\theta_i$ given a fixed amount of data. We determine the
buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
possible unit price. We have,
% BUYER PRICING 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
\end{equation}
where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
We determine that the market supply function is equivalent to buyer demand, and 
acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
% BUYER DEMAND 
\begin{equation}\label{datasupply}
    \rho_i(y) = \sum_{j\in\mcI : p_i^j\le y} D^j.
\end{equation}
We note that $f_i$ is such that
$i$ could still bid in \emph{any} auction $j\in\mcI$.
Therefore, in a coordinated bid, the utility-maximizing bid price is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers. We will later show, in Proposition
\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
bids, i.e. using the same bid for all auctions.
Using buyer bid quantity $e_i^j(a)$, from (\ref{opt-out}), 
we have the following Lemma,
{
% BUYER CONSTRAINTS
\lemma{(Buyer constraints)}\label{buyerconstraints}
Let $i\in\mcI$ be a buyer with bid, $s_i = (e_i(a), p_i)$, which must obey
the following constraints,
\begin{equation}\label{buyercapmax}
    \sum_{j\in\mcI} e^j_i(a) \le D_i,
\end{equation}
and, as $i$ is rational, and therefore utility-maximizing, $i$ must have
sufficient bids $s_i^j > 0$ so that,
\begin{equation}\label{buyercapmin}
    \sum_{j\in\mcI} d^j_i \ge D_i,
\end{equation}
where $d_i^j$ denotes the bid quantity of seller $j$.
}\\
\textbf{Proof:}
A rational buyer does not want to purchase extra data, as this would be
equivalent to overpaying, and so (\ref{buyercapmax}) holds. We also assume that
$i$ wants to fufill their data requirement, and so (\ref{buyercapmin}) implies
that $i$ submits positive bids to a set of buyers that will be able to fufill
their demand.

The seller is similarly represented, however a seller only has
information from buyers in its own auction, and may only be indirectly influenced by
buyers in other auctions. So from the perspective of the
seller we have a more direct interpretation of valuation as revenue.
We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} e_i^j(a), 
\end{equation}
and define the ``inverse" of the buyer demand function for seller $j$ as
potential revenue at unit price $y$, we have, 
% SELLER REVENUE 
\begin{equation}\label{sellerinversedemand}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
price. Now, we determine that, in addition to some natural constraints, the sellers' highest
``possible" price is conditioned by
additional restrictions on its pricing function, the motivation for which is
that a buyer has the choice to opt-out of any auction, and so seller $j$ has an
incentive to set its reserve price to include enough buyers to sell all its
data. Thus we have the following Lemma,
{
% SELLER CONSTRAINTS
\lemma{(Seller constraints)}\label{sellerconstraints}
Let $j\in\mcI$ be a seller with bid $s^j$, then $j$ must obey the following constraints.
A bid $s_i^j= (d_i^j, p_i^j)$, to buyer $i$ must be such that,
\begin{equation}\label{datacapmax}
    \sum_{i\in\mcI} d^j_i \le D^j,
\end{equation}
In addition, for a rational seller, the reserve price must
satisfy, $\forall \ i\in \mcI$,
\begin{equation}\label{reservepricemin}
   p_i^j \ge \min_{i\in\mcI}\big(p_i^j),
\end{equation}
and,
\begin{equation}\label{reservepricemax}
   p_i^j \le \max_{i\in\mcI}\big(p_i^j).
\end{equation}
Finally, as $j$ is rational, $j$ must submit enough bids $s_i^j >0$ so that,
\begin{equation}\label{datacapmin}
    \displaystyle\sum_{i\in\mcI} e_i^j(a) \ge D^j.
\end{equation}
}\\
\textbf{Proof:}
The first statement is obvious, 
a seller cannot sell more data than they have,
Then, (\ref{reservepricemin})
follows from the assumption that $j$ is rational, and so utility-maximization
acts as revenue maximization, a rational seller will not sell its
data at a price less than the lowest offer. Finally, as a rational seller will
attempt to maximize profit, and will try and sell all of its data, and so we
must have sufficient demand
from the buyers. Therefore, (\ref{reservepricemax}) and (\ref{datacapmin}) hold. Together, (\ref{datacapmax}) and
(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} e_i^j(a) >  D^j$. In
this case, by (\ref{dataallocation}), $j$ may submit a partial bid to a buyer
$i$ so that $\sum_{i\in\mcI} d^j_i = D^j$.

>>>>

In applying a distributed PSP implementation to CMHK's secondary market, we
find that
the market is able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and design our mechanism tp provide the functions
for effective communication between the connected users. We claim that in
this secondary market our formulation holds the desired VCG qualities through the construction of a
probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.

@@

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in this secondary market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many ISPs each holding
thier own local auction; there is no entity that holds a global market knowledge.

@@

@@

Progressive second price auctions (PSPs) were proposed
in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
scheme to provide consistent services for network bandwith users.
\cite{diffserve} conducts a game theoretic analysis, deriving
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria based on their game-theoretic
model. Constructing necessary and sufficient conditions for the stability
of the game allows the sustainability of any set
of service level agreement configurations between Internet service
providers to be determined.

@@

% MECHANISM
\subsubsection{The Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
We have the definition of an elastic valuation function. In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}

@@

\section{The Problem Model}
\subsection{The CMHK Market}

We begin to construct the model for a PSP data auction for  mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
 Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which typically
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}. 
As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$.
A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$. 
Finally, we assume that data is a unary resource belonging to the seller, and
therefore can identify each local auction
with the identity of the seller $j\in\mcI$.

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

The main contribution of this work 
is an auction mechanism inspired by the classic PSP throughput problem. In
order to apply a distributed PSP implementation to CMHK's secondary market,
we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the communication
expense from numerous local auctions trading an infinitely divisible resource.
We will assume that the cost of participatingn in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. We perform a simple survey of these bid fee models, we
provide some idea of the expected revenue of the mobile data ISP (NEED
STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
market, additionally, the purchased data expires (does not carry to the next
service period). Therefore, a simple definition of market equilibrium, where
supply equals demand, is insufficent to complete a comprehensive analysis of
the CMHK data-exchange market behavior. We will make an attempt to address why
our formulation at least partially considers some of these issues (BAD), such
as the impact of the bid fee on user behavior. (MOVE SOME OF THIS UP)
Finally, we  .... (WHAT? COMPLETE THE THOUGHT)

We claim that the market is
able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, our mechanism provides the functions
for the effective communication between the connected users. It was shown in
\cite{lazar} that a $2$-dimensional message space is sufficient for the PSP
auction. Using a restricted message space is essential for the distributed
nature of our design (EXPLAIN), however, as a given message can come from many
possible types, there is no single
way to do the transformation from the direct revelation mechanism to the
desired one. This is equivalent to guessing the
right direct-revelation-to-desired-mechanism transformation and building it
into the allocation rule from the start. (FINISH!)
We claim that in
this secondary market our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead (and so possibly fees paid to the ISP)
and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
with respect to the classic throughput problem.

@@

We are not concerned with network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
we reason that there remains an optimal user strategy. As a user no longer needs
to bid on a complete (but arbitrary)
cluster of nodes with minimum bandwidth allocation (defined as a route in
\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
its market behavior. In a general sense, $e$ applies our user \emph{strategy}
to the PSP rules.
Our reserve price function is determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers. We demonstrate that as the valuation function of seller $j$ is dependent
on the buyers demand, and further show evidence of symmetry in the strategies of
buyers and sellers.
